---
title: "Midterm exam"
author: "Chantsal 108035487"
date: "4/27/2020"
output: html_document
---
# Download ETF daily data from yahoo with ticker names of SPY, QQQ, EEM, IWM, EFA, TLT, IYR, GLD from 2010 to 2018. 
```{r}
rm(list=ls())
library(quantmod)
library(quadprog)
library(lpSolve)
con = gzcon(url('https://github.com/systematicinvestor/SIT/raw/master/sit.gz', 'rb'))
source(con)
close(con)
tickers <- c('SPY','QQQ','EEM','IWM','EFA','TLT','IYR','GLD')
data <- new.env()
getSymbols(tickers, src = 'yahoo', from = '2010-01-01',to= '2018-12-31', env = data, auto.assign = T)
for(i in ls(data)) data[[i]] = adjustOHLC(data[[i]], use.Adjusted=T)

bt.prep(data, align='remove.na', fill.gaps = T)
names(data)
head(data$prices)
head(data$weight)

```


## Q1. Use the data to calculate daily returns. Find their means, median, 1-st quartile, third-quartile, standard deviation, skewness and kurtosis.
```{r}
prices = data$prices   
n = ncol(prices)
n

ret = prices / mlag(prices) - 1
ret

means= mean(prices)
means

median(prices)

sqrt(var(prices))

sd(prices)

Sigma= cov(prices)
std = sqrt(diag(Sigma))

quantile(prices)

library(moments)
skewness(prices)

kurtosis(prices)

```

## Q2. Based on daily returns and their covariance matrix, and compute weights of minimum variance portfolio (MVP). 
```{r}
str(prices)
Sigma = cov(prices)
std = sqrt(diag(Sigma))
ones = rep(1,8)     
one.vec = matrix(ones, ncol=1)
a = inv(Sigma)%*%one.vec
b = t(one.vec)%*%a
mvp.w =a / as.numeric(b)
mvp.w
mvp.ret<-sum((mvp.w)*colMeans(prices))
mvp.ret


```

## Q3.By 2, now use year 2010-2013 data to calculate weekly returns and their covariance matrix, and compute weights of minimum variance portfolio (MVP).  (hints: you can use endpoints() to find weekly and monthly data. 

```{r}
library(xts)
data.weekly <- ret[endpoints(ret, on="weeks", k=1), ]
str(data.weekly)
Sigma.w = cov(data.weekly)
std = sqrt(diag(Sigma.w))
ones = rep(1,8)     
one.vec = matrix(ones, ncol=1)
a = inv(Sigma.w)%*%one.vec
b = t(one.vec)%*%a
mvp.w.w =a / as.numeric(b)
mvp.w.w
mvp.ret.w<-sum((mvp.w.w)*colMeans(data.weekly))
mvp.ret.w

```

## Q4.  By 3, now use year 2010-2013 data to calculate monthly returns and their covariance matrix, and compute weights of minimum variance portfolio (MVP). 
```{r}
data.monthly <- ret[endpoints(ret, on="months", k=1), ]
str(data.monthly)
Sigma.m = cov(data.monthly)
std = sqrt(diag(Sigma.m))
ones = rep(1,8)     
one.vec = matrix(ones, ncol=1)
a = inv(Sigma.m)%*%one.vec
b = t(one.vec)%*%a
mvp.w.m =a / as.numeric(b)
mvp.w.m
mvp.ret.m<-sum((mvp.w.m)*colMeans(data.monthly))
mvp.ret.m
```

## Q5. Compute optimal weights for Q3 and Q4 when short selling is not allowed.
```{r}


```

## Q6. Go to Fama French 3 factors data website:
```{r}
#a.	Compute its mean and covariance matrix using monthly data from 2010-2018.
library(tidyverse)
retdata= read_csv('F-F_Research_Data_Factors.CSV')
colnames(retdata)[2]<- 'Mkt_RF'
stock.rets<-retdata %>% select(c(2,3,4,5))/100
N <- dim(stock.rets)[1]
fit3 = lm(formula = cbind(RF)~Mkt_RF + SMB + HML, data=stock.rets)
sigF3 = as.matrix(var(cbind(stock.rets$Mkt_RF, 
                            stock.rets$SMB, 
                            stock.rets$HML)))
bbeta3 = as.matrix(fit3$coefficients)
bbeta3 = bbeta3[-1,]
bbeta3
sigeps3 = crossprod(fit3$residuals)/(N-4)
sigeps3 = diag(diag(sigeps3))

X.3 = cbind(ones, stock.rets$Mkt_RF, stock.rets$SMB, stock.rets$HML)
retdata1 = as.matrix(retdata[,c(2,3,4)]/100)
b_hat.3 = solve(t(X.3)%*%(X.3))%*%t(X.3)%*%retdata1
E_hat.3 = retdata1 - X.3%*%b_hat.3
b_hat.3 = as.matrix(b_hat.3[-1,])
diagD_hat.3 = diag(t(E_hat.3)%*%E_hat.3)/(N-4)
cov_3f.3 = t(b_hat.3)*sigF3*b_hat.3 + diag(diagD_hat.3) 
cov_3f.3

# b.	Plot the returns of three factors from 2010-2018.


```

## Q7. Based on CAPM model, compute covariance matrix for the 8-asset portfolio by using past 60 monthly returns from 2014/01 - 2018/12.
```{r}

```


## Q8. Based on FF 3-factor model, compute covariance matrix for the 8-asset portfolio by using past 60 monthly returns.
```{r}

```

## Q9. Compute global minimum variance portfolio weights based on Q7 and Q8.
```{r}

```

